Modelling BCG vaccination in the UK

### 2019-08-07 rmds/05-evidence-policy-change.Rmd
sutherland updated based on reviewer comments

$$ Z = \frac{xz + x^{2}2z + x^{3}3z + . .}{x+x^2+x^3+ . . }= \frac{z}{1-x} $$
#### Transmission chain model additions

@@

Where $P$ is the number of primary notifications, $i$ is the year of interest, $N^{Current}$ is the number of secondary cases in the current  year, $N^{Projected}$ is the number of secondary cases in the subsequent timestep, and $L$ is the model timestep (here set to be 5).

>>>>

$$ Z = \frac{xz + x^{2}2z + x^{3}3z + . .}{x+x^2+x^3+ . . }= \frac{z}{1-x} $$

#### Transmission chain model additions

@@

Where $P$ is the number of primary notifications, $i$ is the year of interest, $N^{Current}$ is the number of secondary cases in the current  year, $N^{Projected}$ is the number of secondary cases in the subsequent timestep, and $L$ is the model timestep (set to be 5 years).
